Rate Transfers with Polyhedral Surrogate Losses /\\ Surrogate Regret Bounds for Polyhedral Losses

### 2021-05-13 rates-neurips-21/rates.tex
small comments on setting

\paragraph{Surrogate regret bounds.}
Given a target problem, we would like to design surrogates which efficiently solve it.
A standard tool to establish this efficiency is a \emph{surrogate regret bound}.
We define the \emph{regret} of a hypothesis $h: \X \to \reals^d$ as the expected loss relative to the best possible.
Formally, for a surrogate $L$, the regret of $h$ with respect to data distribution $\D$ is given by $R_L(h;\D) = E_{(X,Y)\sim\D} L(h(X), Y) - \inf_{h':\X\to\reals^d} E_{(X,Y)\sim\D} L(h'(X),Y)$, where the minimum is taken over all measurable functions.
(One may equivalently assume the Bayes optimal hypothesis is in the function class.)
The target regret of $h$ is thus $R_\ell(\psi\circ h;\D) = E_{(X,Y)\sim\D} \ell(\psi(h(X)), Y) - \inf_{h':\X\to\R} E_{(X,Y)\sim\D} \ell(h'(X),Y)$, where we recall that $\psi$ is the link function.

A surrogate regret bound answers the following question: if we can minimize the true surrogate regret at a rate $f(n)$, given $n$ data points, how fast does the corresponding hypothesis $h_n$ minimize the target regret?
Formally, a surrogate regret bound is given by a function $\zeta : \reals_+ \to \reals_+$, such that
\begin{equation}
  \label{eq:surrogate-regret-bound}
  \forall \D, \forall h:\X\to\reals^d, \quad R_\ell(\psi\circ h;\D) \leq \zeta(\, R_L(h;\D) \,)~.
\end{equation}
A minimal requirement is that $(L,\psi)$ is \emph{consistent} with $\ell$, meaning $\zeta$ is continuous at $0$ and satisfies $\zeta(0) = 0$.

@@

\end{theorem}
The second is that sufficiently convex and smooth losses (i.e., ``non-polyhedral'') require $\zeta(\epsilon) = \Omega(\sqrt{\epsilon})$.
\begin{theorem}

>>>>

\paragraph{Surrogate regret bounds.}
Given a target problem, we would like to design surrogates which efficiently solve it.
A standard tool to establish this efficiency is a \emph{surrogate regret bound}.
We define the \emph{regret} of a hypothesis $h: \X \to \reals^d$ as the expected loss relative to the best possible.
Formally, the \emph{surrogate regret} of $h$ with respect to data distribution $\D$ is given by $R_L(h;\D) = E_{(X,Y)\sim\D} L(h(X))_Y - \inf_{h':\X\to\reals^d} E_{(X,Y)\sim\D} L(h'(X))_Y$, where the minimum is taken over all measurable functions.
\bo{Notation changed: $L(h(X),Y) \to L(h(X))_Y$.}
(One may equivalently assume the Bayes optimal hypothesis is in the function class.)
The \emph{target regret} of $h$ is thus $R_\ell(\psi\circ h;\D) = E_{(X,Y)\sim\D} \ell(\psi(h(X)))_Y - \inf_{h':\X\to\R} E_{(X,Y)\sim\D} \ell(h'(X))_Y$, where we recall that $\psi$ is the link function.

A surrogate regret bound answers the following question: when we minimize the surrogate regret at a rate $f(n)$, given $n$ data points, how fast does the target regret diminish?
Formally, a surrogate regret bound is given by a function $\zeta : \reals_+ \to \reals_+$, such that
\bo{Why drop the definition ``transfer function''? I think it's very useful here.}
\begin{equation}
  \label{eq:surrogate-regret-bound}
  \forall \D, \forall h:\X\to\reals^d, \quad R_\ell(\psi\circ h;\D) \leq \zeta(\, R_L(h;\D) \,)~.
\end{equation}
A minimal requirement is that $(L,\psi)$ is \emph{consistent} with $\ell$, meaning $\zeta$ is continuous at $0$ and satisfies $\zeta(0) = 0$.

\bo{I think the discussion I had on sqrt and fast rates would be useful...}

@@

\end{theorem}
The second is that sufficiently convex and smooth losses (i.e., ``non-polyhedral'') require $\zeta(\epsilon) = \Omega(\sqrt{\epsilon})$.

\begin{theorem}
